Data Migration under a Changing Schema

### 2023-07-10 2022Migration/articleMigrationFACS.tex
wip

   A problem is that software generators typically do not support the data migration process, especially when the schema changes.
   The ``manual'' effort required to migrate data slows down the development process and introduces mistakes%
   Such effects can be measured in terms of DevOps metrics such as deployment frequency, reliability of deployments, and change failure rate~\cite{DevOps2021}.

>>>>

   A problem is that software generators typically do not support the data migration process, especially when the schema changes.
   The ``manual'' effort required to migrate data slows down the development process and introduces mistakes.
   Such effects can be measured in terms of DevOps metrics such as deployment frequency, reliability of deployments, and change failure rate~\cite{DevOps2021}.
